---
title: "Introduction to {altcheckr} functions"
author: "Matt Dray"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")

library(altcheckr)
library(dplyr)
```

# Install

You can install {altcheckr} from GitHub using the {remotes} package.

```{r install, eval=FALSE}
install.packages(remotes)
install_github("matt-dray/altcheckr")
library(altcheckr)
```

# Get image elements

Use the `alt_get()` function to scrape the attributes of each <img> element
on a web page that you name in the `url` argument,

The function uses {xml2} and {rvest} to scrape a given web page and extract
image attributes, with a little bit of {purrr} to get it into a data frame.

```{r get}
get_img <- alt_get("https://www.bbc.co.uk/news")
```

The function returns a tibble where each row is an image element from that page
and columns are the the image source (`src`), alt text (`alt`) and link to a
file with a longer description (`longdesc`), if it exists (sometimes used for
complex images). The `alt` column will be created and filled with `NA` if it
isn't present.

Setting the argument `all_attributes` to `TRUE` will return all the attributes
provided in the <img> element, not just `src`, `alt` and `longdesc`.

Here is a preview of the tibble that is output from `alt_get()`:

```{r get-print}
print(get_img)
```

# Check alt text

You can then pass the output of `alt_get()` to `alt_check()` to perform a series of
basic assessments of each image's alt text.

(You can also pass any data frame that contains a `src` and `alt` column, where
`alt` contains the text to be assessed by `alt_check()`. For example,
{altcheckr} has a built-in dataset: `example_get`.)

```{r check}
check_img <- alt_check(get_img)
```

This will return the same tibble as `alt_get()`, but new columns have now been
appended.

Each new column is the outcome of a check for a possible accessibility issue
with the alt text. For example, whether the alt text actually exists and whether
it is long.

```{r check-print}
print(check_img)
```

And here is the structure now:

```{r check-str}
dplyr::glimpse(check_img)
```
